InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-05 paper.tex
Include suggested rephrasings

\section{Introduction}
The development of generative Machine Learning models made huge steps forward in the last years, considering the comparison with human crafted artefacts. Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles. Image generating models like Vision Transformer (ViT) models already created fake images being reported as real by media. Other news showed artists winning art competitions with generated art. This creates an interest in detecting which texts or images are AI generated and which ones are real images or human-written texts.

Therefore researchers evaluated different approaches to detect fake images and texts. Fortunately some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e. g. visual object detection, by artificially manipulating real images. This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g. images and texts) to reduce the accuracy of detectors.

It is necessary to evaluate whether such techniques exist, because otherwise one could rely on detectors, which can easily be tricked. If easy efficient manipulation techniques exist, existing detectors need to be improved or better detectors need to be developed that are robust against these techniques. But this preconditions a good understanding of the way attacks are performed.

@@

The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generating models as well as fake image and text detectors. Chapter 3 presents the methodology of our work followed by chapter 4 presenting the results of our experiments. Afterwards the results will be discussed in chapter 5 and chapter 6 will conclude the work.

>>>>

\section{Introduction}
The development of generative Machine Learning models made huge steps forward in the last years, considering the comparison with human crafted artefacts. Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles. Image generating models like Vision Transformer (ViT) already created fake images being reported as real by media. Other news showed artists winning art competitions with generated art. This creates an interest in detecting which texts or images are AI generated and which ones are real images or human-written texts.

Therefore researchers evaluated different approaches to detect fake images and texts. Some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e. g. visual object detection, by artificially manipulating real images. This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g. images and texts) to reduce the accuracy of detectors.

It is necessary to evaluate whether such techniques exist, because otherwise one could rely on detectors, which can easily be tricked. If easy efficient manipulation techniques exist, detectors need to be improved or better detectors need to be developed that are robust against these techniques. But this requires a good understanding how the attacks are performed.

@@

The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generating models as well as fake image and text detectors. Chapter 3 presents the methodology of our work followed by chapter 4 presenting the results of our experiments. Afterwards the results will be discussed in chapter 5 and chapter 6 will conclude this paper.
